Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.

### 2022-02-11 ASME_journal/journals-1.0/journals-1.0/TSEA-21-1636_FINAL_SUBMISSION.tex
Update-11/02/2022

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aeronautical Engineering %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[twocolumn,10pt]{asme2ej}

\usepackage{graphicx} %% for loading jpg figures
\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}

\newcommand{\highlight}[1]{%
  \colorbox{yellow!}{$\displaystyle#1$}}
%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

@@

%%% first author
\author{Brad T. Rawlins\thanks{Corresponding author}
    \affiliation{
	Ph.D. Candidate\\
	Department of Mechanical \\Engineering\\
	University of Cape Town\\
    Email: rwlbra001@myuct.ac.za
    \vspace{5mm}
    }

}

@@

\begin{nomenclature}
\entry{}{\textit{Variables}}
\entry{$A$}{Area [$m^2$]}
\entry{$A_p$}{Particle surface area [$m^2$]}
\entry{$A_{pn}$}{Projected particle surface area [$m^2$]}
\entry{$A_{c}$}{Carbon pre-exponential factor [$s^{-1}$]}
\entry{$A_{vol}$}{Volatile pre-exponential factor [$s^{-1}$]}
\entry{$d_p$}{Particle diameter [$m$]}
\entry{$E$}{Fluid total energy [$J/kg$]}
\entry{$E_{a,c}$}{Carbon activation energy [$J/kmol$]}
\entry{$E_{a,vol}$}{Volatile activation energy [$J/kmol$]}
\entry{$E_p$}{Particle emission power [$W/m^3$]}
\entry{$f_{heat}$}{Near surface char oxidation fraction [$-$]}
\entry{$f_{p}$}{Forward scattering factor [$-$]}
\entry{$G$}{Incident radiation [$W/m^2$]}
\entry{$g$}{Gravitational constant [$m/s^2$]}
\entry{$h_{fg}$}{Enthalpy of evaporation [$J/kg$]}
\entry{$h_M$}{Mixture enthalpy [$J/kg$]}
\entry{$h_{rxn}$}{Enthalpy of reaction [$J/kg$]}
\entry{$J_k$ }{Species diffusion flux [$m^2/s$]}
\entry{$m_{0,vol}$}{Original mass of volatiles [$kg$]}
\entry{$m_{char}$}{Mass of carbon [$kg$]}
\entry{$m_{evap}$}{Mass of moisture [$kg$]}
\entry{$m_{vol}$}{Mass of volatiles [$kg$]}
\entry{$N_{p}$}{Number of particles [$-$]}
\entry{$P$}{Perimeter [$m$]}
\entry{$p$}{Pressure [$Pa$]}
\entry{$p_{O_{2}}$}{Partial pressure of $O_2$ [$Pa$]}
\entry{$\dot{Q}_{conv}$}{Convective heat transfer rate [$W$]}
\entry{$\dot{Q}_{rad}$}{Radiative heat transfer rate [$W$]}
\entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
\entry{$R$}{Universal gas constant [$J/molK$]}
\entry{$R_{c}$}{Carbon reaction rate [$s^{-1}$]}
\entry{$R_{diff}$}{Diffusion reaction rate [$s^{-1}$]}
\entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
\entry{$S$}{\hl{Mass source term}[$kg/m^3$]}
\entry{$S_m$}{\hl{Momentum source term} [$/m^3$]}
\entry{$S_h$}{\hl{Energy source term} [$W/m^3$]}
\entry{$S_k$}{\hl{Species source term} [$kg/m^3$]}
\entry{$T_g$}{Gas temperature [$K$]}
\entry{$T_p$}{Particle temperature [$K$]}
\entry{$t$}{Time [$s$]}
\entry{$u$}{Velocity [$m/s$]}
\entry{$V$}{Volume [$m^3$]}
\entry{$Y_k$}{Species mass fraction [$kg/kg$]}
\entry{$x$}{Quality [$-$]}
\entry{}{\textit{Greek Variables}}
\entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
\entry{$\alpha_H$}{Mixture void fraction [$-$]}
\entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
\entry{$\epsilon_p$}{Particle emissivity [$-$]}
\entry{$\rho$}{Gas density [$kg/m^3$]}
\entry{$\rho_{eff}$}{Effective density [$kg/m^3$]}
\entry{$\rho_g$}{Gas density [$kg/m^3$]}
\entry{$\rho_l$}{Liquid density [$kg/m^3$]}
\entry{$\rho_M$}{Mixture density [$kg/m^3$]}
\entry{$\rho_p$}{Particle density [$kg/m^3$]}
\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
\entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
\entry{$\phi$}{Scalar variable [$-$]}
\entry{}{\textit{Abbreviations}}
\entry{$MCR$}{Maximum continuous rating}
\entry{$CFPP$}{Coal fired power plant}
\entry{$CFD$}{Computational fluid dynamics}
\entry{$SH$}{Superheater}
\entry{$EE$}{Eulerian-Eulerian}
\entry{$WSGGM$}{Weighted sum of gray gas model}
\entry{$RTE$}{Radiative transport equation}
\entry{$HHV$}{Higher heating value}
\entry{$DAF$}{Dry ash free}
\entry{$AR$}{As-received}
\entry{$PA$}{Primary air}
\entry{$SA-AH$}{Secondary air - air heater}
\entry{$SA$}{Secondary air}
\entry{$RH$}{Reheater}
\entry{$ATT$}{Attemperator}
\entry{$EC$}{Economiser}
\end{nomenclature}
\section{Introduction}
The use of coal-fired power plants (CFPP) for electricity generation is intended to be phased out to reduce the rate of climate change. However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.\\

@@

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\
\newpage
The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\

@@

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. \hl{The governing equations for the gas phase are written below in their respective Reynolds averaged forms}.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=\highlight{S}
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\\
&\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{split}
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

@@

A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\
\newpage
The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}. Both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash. The scalar field equations are provided in Table \ref{tab_scalars}.\\

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabularx}
\end{table}

@@

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. \hl{To solve the additional transport equations and their source terms user defined functions, utilized by ANSYS Fluent, were developed using the C programming language.}

\subsection{Heat transfer modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\begin{split}
&\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \\
&\frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{split}
\end{equation}
In the present work the RTE is solved using the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aerospace Engineering    %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Modified: July 19, 2009 as a template in a single column for       %
%           ASME Journals by Harry H. Cheng                          %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use 10pt options with the asme2ej format
\documentclass[10pt]{asme2ej}

\usepackage{epsfig} %% for loading postscript figures
\usepackage{graphicx} %% for loading jpg figures
\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}

%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

@@

%%% first author
\author{Brad T. Rawlins\thanks{Corresponding author}
    \affiliation{
	Ph.D. Candidate\\
	Department of Mechanical \\Engineering\\
	University of Cape Town\\
    Email: rwlbra001@myuct.ac.za
    \vspace{5mm}
    }	
    }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\begin{multicols}{2}
\entry{\textbf{\textit{Variables}}}{}
\entry{$A$}{Area [$m^2$]}
\entry{$A_p$}{Particle surface area [$m^2$]}
\entry{$A_{pn}$}{Projected particle surface area [$m^2$]}
\entry{$A_{c}$}{Carbon pre-exponential factor [$s^{-1}$]}
\entry{$A_{vol}$}{Volatile pre-exponential factor [$s^{-1}$]}
\entry{$d_p$}{Particle diameter [$m$]}
\entry{$E$}{Fluid total energy [$J/kg$]}
\entry{$E_{a,c}$}{Carbon activation energy [$J/kmol$]}
\entry{$E_{a,vol}$}{Volatile activation energy [$J/kmol$]}
\entry{$E_p$}{Particle emission power [$W/m^3$]}
\entry{$f_{heat}$}{Near surface char oxidation fraction [-]}
\entry{$f_{p}$}{Forward scattering factor [-]}
\entry{$G$}{Incident radiation [$W/m^2$]}
\entry{$g$}{Gravitational constant [$m/s^2$]}
\entry{$h_{fg}$}{Enthalpy of evaporation [$J/kg$]}
\entry{$h_M$}{Mixture enthalpy [$J/kg$]}
\entry{$h_{rxn}$}{Enthalpy of reaction [$J/kg$]}
\entry{$J_k$ }{Species diffusion flux [$m^2/s$]}
\entry{$m_{0,vol}$}{Original mass of volatiles [$kg$]}
\entry{$m_{char}$}{Mass of carbon [$kg$]}
\entry{$m_{evap}$}{Mass of moisture [$kg$]}
\entry{$m_{vol}$}{Mass of volatiles [$kg$]}
\entry{$N_{p}$}{Number of particles [-]}
\entry{$P$}{Perimeter [$m$]}
\entry{$p$}{Pressure [$Pa$]}
\entry{$p_{O_{2}}$}{Partial pressure of $O_2$ [$Pa$]}
\entry{$\dot{Q}_{conv}$}{Convective heat transfer rate [$W$]}
\entry{$\dot{Q}_{rad}$}{Radiative heat transfer rate [$W$]}
\entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
\entry{$q_{wall}$}{Wall heat flux [$W/m^2$]}
\entry{$R$}{Universal gas constant [$J/molK$]}
\entry{$R_{c}$}{Carbon reaction rate [$s^{-1}$]}
\entry{$R_{diff}$}{Diffusion reaction rate [$s^{-1}$]}
\entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
\entry{$S$}{Mass source term[$kg/m^3$]}
\entry{$S_m$}{Momentum source term [$N/m^3$]}
\entry{$S_h$}{Energy source term [$W/m^3$]}
\entry{$S_k$}{Species source term [$kg/m^3$]}
\entry{$T_g$}{Gas temperature [$K$]}
\entry{$T_p$}{Particle temperature [$K$]}
\entry{$T_{wall,i}$}{Wall temperature [$K$]}
\entry{$T_{water}$}{Water temperature [$K$]}
\entry{$t$}{Time [$s$]}
\entry{$U_i$}{Over heat transfer coefficient [$W/m^2K$]}
\entry{$u$}{Velocity [$m/s$]}
\entry{$V$}{Volume [$m^3$]}
\entry{$Y_k$}{Species mass fraction [$kg/kg$]}
\entry{$x$}{Quality [-]}
\entry{\textbf{\textit{Greek Variables}}}{}
\entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
\entry{$\alpha_H$}{Mixture void fraction [-]}
\entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
\entry{$\epsilon_p$}{Particle emissivity [-]}
\entry{$\rho$}{Gas density [$kg/m^3$]}
\entry{$\rho_{eff}$}{Effective density [$kg/m^3$]}
\entry{$\rho_g$}{Gas density [$kg/m^3$]}
\entry{$\rho_l$}{Liquid density [$kg/m^3$]}
\entry{$\rho_M$}{Mixture density [$kg/m^3$]}
\entry{$\rho_p$}{Particle density [$kg/m^3$]}
\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
\entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
\entry{$\phi$}{Scalar variable [-]}
\entry{\textbf{\textit{Abbreviations}}}{}
\entry{$MCR$}{Maximum continuous rating}
\entry{$CFPP$}{Coal fired power plant}
\entry{$CFD$}{Computational fluid dynamics}
\entry{$SH$}{Superheater}
\entry{$EE$}{Eulerian-Eulerian}
\entry{$WSGGM$}{Weighted sum of gray gas model}
\entry{$RTE$}{Radiative transport equation}
\entry{$HHV$}{Higher heating value}
\entry{$DAF$}{Dry ash free}
\entry{$AR$}{As-received}
\entry{$PA$}{Primary air}
\entry{$SA$-$AH$}{Secondary air - air heater}
\entry{$SA$}{Secondary air}
\entry{$RH$}{Reheater}
\entry{$ATT$}{Attemperator}
\entry{$EC$}{Economiser}
\end{multicols}
\end{nomenclature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The use of coal-fired power plants (CFPP) for electricity generation is intended to be phased out to reduce the rate of climate change. However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.\\

@@

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\

@@

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
The present CFD work makes use of a Eulerian-Eulerian approach to capture the distribution of solid and gaseous phase properties such as mass fractions and velocities. The approach is similar to that of the mixture model supplied in ANSYS Fluent v19.5\textsuperscript{\textregistered}, where a single momentum equation is solved for the different phases in the heterogenous mixture. The main difference between the model applied in the current work and the standard mixture model is that the latter solves a single energy equation, whereas the former solves two energy equations, one for the gas phase and another for the solid phase. This is an important feature as it allows the adequate resolution of the temperature-dependent solid fuel combustion processes such as devolatilization and char oxidation, and accurate prediction of particulate radiative heat transfer. Typically, in solid fuel combustion processes the particulate temperature is higher than the surrounding gas temperatures due to the energy release from surface combustion, and incident radiation.
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds averaged forms.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

@@

A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\

The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in Eqn. (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in Eqn. (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of Eqn. (\ref{eqn_char_rate}) are defined in Eqn. (\ref{eqn_char_diff_rate})  and Eqn. (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}. Both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash. The scalar field equations are provided in Tab. \ref{tab_scalars}.\\

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabularx}{0.6\textwidth}{p{0.4in} p{0.3\textwidth} l}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabularx}
\end{table}

@@

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. To solve the additional transport equations and their source terms, user defined functions utilized by ANSYS Fluent, were developed using the \textit{C/C++} programming language.

\subsection{Heat transfer modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in Eqn. (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}

In the present work the RTE is solved using the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}
